---
output: rmarkdown::github_document
---

`hgr` : Tools to Work with the 'Postlight' 'Mercury' 'API'

Mercury takes any web article and returns only the relevant content — headline, author, body text, relevant images and more — free from any clutter. You need an API key which you can get from [here](https://mercury.postlight.com).

The following functions are implemented:

- `just_the_facts`:	Retrieve parsed content of a URL processed by the Postlight Mercury API

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/hgr")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(hgr)

# current verison
packageVersion("hgr")

story <- "https://www.nytimes.com/2017/04/18/world/asia/aircraft-carrier-north-korea-carl-vinson.html?hp&action=click&pgtype=Homepage&clickSource=story-heading&module=first-column-region&region=top-news&WT.nav=top-news&_r=0"

dplyr::glimpse(just_the_facts(story))

```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(hgr)
library(testthat)

date()

test_dir("tests/")
```

